Exponential Integrals\\ [1ex]

### 2022-02-22 draft2.tex

\section{Fractional derivatives and Borel transform}
For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{x \text{ from } 0}$ is defined by
\[ \partial^{\nu-1}_{x \text{ from } 0} f(x) \defeq \frac{1}{\Gamma(1-\nu)} \int_0^x (x-x')^{-\nu} f(x')\,dx'. \]
It obeys the expected semigroup law \textbf{[Lazarevi\'{c}, \S 1.3]}
\begin{align*}
\partial^{\lambda}_{x \text{ from } 0}\,\partial^{\mu}_{x \text{ from } 0} & = \partial^{\lambda+\mu}_{x \text{ from } 0} & \lambda, \mu \in (-\infty, 0),
\end{align*}
and agrees with ordinary repeated integration when $\nu$ is an integer \textbf{[Lazarevi\'{c}, equation~35]}.

For $\alpha \in (0, 1)$ and integers $n \ge 0$, fractional derivatives $\partial^{n+\alpha}_{x \text{ from } 0}$ are defined by composing $\partial^{\alpha-1}_{x \text{ from } 0}$ with powers of $\tfrac{\partial}{\partial x}$. However, $\partial^{\alpha-1}_{x \text{ from } 0}$ and $\tfrac{\partial}{\partial x}$ don't commute: their commutator is an initial value operator \textbf{[check, clarify]}. Various ordering conventions give various definitions of $\partial^{n+\alpha}_{x \text{ from } 0} f(x)$, which differ by operators that act on the germ of $f$ at zero \textbf{[Lazarevi\'{c}, \S 1.3---original source Podlubny]}. We'll use the {\em Riemann-Liouville} convention.
\begin{definition}
For $\alpha \in (0, 1)$ and integers $n \ge 0$, the {\em Riemann-Liouville fractional derivative} $\partial^{n+\alpha}_{x \text{ from } 0}$ is defined by
\[ \partial^{n+\alpha}_{x \text{ from } 0} \defeq \left(\tfrac{\partial}{\partial x}\right)^{n+1} \partial^{\alpha-1}_{x \text{ from } 0}. \]
\end{definition}
The symbol $\partial^\mu_{\zeta \text{ from } 0}$ is now defined for any $\mu \in \R \smallsetminus \{0, 1, 2, 3, \ldots\}$. It denotes a fractional integral when $\mu$ is negative, and a fractional derivative when $\mu$ is a positive non-integer.

The Riemann-Liouville fractional derivative is a left inverse of the fractional integral, in the sense that $\partial^\lambda_{x \text{ from } 0}\,\partial^{-\lambda}_{x \text{ from } 0}$ for all $\lambda \in (0, \infty)$. This extends the semigroup law:
\begin{align*}
\partial^{\lambda}_{x \text{ from } 0}\,\partial^{\mu}_{x \text{ from } 0} & = \partial^{\lambda+\mu}_{x \text{ from } 0} & \lambda \in \R \smallsetminus \{0, 1, 2, 3, \ldots\},\quad\mu \in (-\infty, 0).
\end{align*}

Each convention for the fractional derivative brings its own annoyances to interactions with the Borel transform.\footnote{See Remark~\ref{rmk:caputo} for examples.} The Riemann-Liouville derivative will be the least annoying for our purposes. Here's what's nice about it.
\begin{theorem}
Given a Gevrey-$1$ formal series $\varphi(z) = \sum_{k \ge 0}a_kz^{-(k+1)}$, we have
\[ \partial^\mu_{\zeta \text{ from } 0} \left[ \borel \varphi \right](\zeta) = \left[ \borel z^\mu \varphi \right](\zeta) \]
for any $\mu \in \R \smallsetminus \{0, 1, 2, 3, \ldots\}$.
\end{theorem}
\color{Turquoise}
Here's how we'll use this later. By definition, $\tilde{I}_p(z) = z^{-1/2}\tilde{\varphi}_p(z)$, so the theorem gives
\begin{align*}
\left[ \borel_{\zeta_\alpha} \tilde{I}_p \right](\zeta) & = \left[ \borel_{\zeta_\alpha} z^{-1/2} \tilde{\varphi}_p \right](\zeta) \\
& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \left[ \borel \tilde{\varphi}_p \right](\zeta) \\
& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_p(\zeta).
\end{align*}
Once we show that $\borel \tilde{I}_p = \hat{I}_p$, we have
\begin{align*}
\hat{I}_p(\zeta) & = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_p(\zeta) \\
\partial^{-1}_{\zeta \text{ from } \zeta_\alpha} \hat{I}_p(\zeta) & = \partial^{-3/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_p(\zeta)
\end{align*}
thanks to the semigroup law. Once we show that
\[ \hat{I}_p(\zeta) = \tfrac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_p(\zeta)} \nu \right), \]
we can deduce that
\[ \partial^{-1}_{\zeta \text{ from } \zeta_\alpha} \hat{I}_p(\zeta) = \int_{\mathcal{C}_p(\zeta)} \nu - \int_{\mathcal{C}_p(0)} \nu. \]
The path $\mathcal{C}_p(0)$ is a point, so the initial value term vanishes, and we can conclude that
\[ \int_{\mathcal{C}_p(\zeta)} \nu = \partial^{-3/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_p(\zeta). \]
Finally, recalling that the Riemann-Liouville fractional derivative is a left inverse of the fractional integral, we see that
\[ \partial^{3/2}_{\zeta \text{ from } \zeta_\alpha} \int_{\mathcal{C}_p(\zeta)} \nu = \hat{\varphi}_p(\zeta). \]
\color{black}

\begin{lemma}
For any non-integer $\mu \in (0, \infty)$ and any integer $k \ge 0$,
\[ \partial^\mu_{\zeta \text{ from } 0} \left[ \borel z^{-(k+1)} \right](\zeta) = \left[ \borel z^\mu z^{-(k+1)} \right](\zeta). \]
\end{lemma}
\begin{proof}
We'll show that for any $\alpha \in (0, 1)$ and any integer $n \ge 0$, the claim holds with $\mu = n + \alpha$. First, evaluate
\begin{align*}
\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel z^{-(k+1)} \right](\zeta) & = \frac{1}{\Gamma(1-\alpha)} \int_0^\zeta (\zeta-\zeta')^{-\alpha} \frac{{\zeta'}^k}{\Gamma(k+1)}\,d\zeta' \\
& = \frac{1}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (\zeta-\zeta t)^{-\alpha} (\zeta t)^k\,\zeta\,dt \\
& = \frac{\zeta^{k-(\alpha-1)}}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (1-t)^{-\alpha} t^k\,dt \\
& = \frac{\zeta^{k-(\alpha-1)}}{\Gamma\big(k-(\alpha-1)+1\big)}
\end{align*}
by reducing the integral to Euler's beta function \textbf{[DLMF 5.12.1]}. This establishes that
\begin{equation}\label{frac-diff-laplace}
\left(\tfrac{\partial}{\partial \zeta}\right)^{n+1}\,\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel z^{-(k+1)} \right](\zeta) = \frac{\zeta^{k-(n+\alpha)}}{\Gamma\big(k-(n+\alpha)+1\big)}
\end{equation}
for $n = -1$. If \eqref{frac-diff-laplace} holds for $n = m$, it also holds for $n = m+1$, because
\begin{align*}
\tfrac{\partial}{\partial \zeta} \left(\tfrac{\partial}{\partial \zeta}\right)^{m+1}\,\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel z^{-(k+1)} \right](\zeta) & = \tfrac{\partial}{\partial \zeta} \left( \frac{\zeta^{k-(m+\alpha)}}{\big(k-(m+\alpha)\big)\,\Gamma\big(k-(m+\alpha)\big)} \right) \\
& = \frac{\zeta^{k-(m+1+\alpha)}}{\Gamma\big(k-(m+\alpha)\big)}
\end{align*}
Hence, \eqref{frac-diff-laplace} holds for all $n \ge -1$, and the desired result quickly follows. The condition $\alpha \in (0, 1)$ saves us from the trouble we'd run into if $k-(m+\alpha)$ were in $\Z_{\le 0}$. This is how we avoid the initial value corrections that appear in ordinary derivatives of Borel transforms.
\end{proof}
\color{MidnightBlue}
\begin{definition}
Let $\alpha\in (0,1)$ and $n\in\N$, then the $n+\alpha$-Caputo's derivative of a smooth fucntion $f$ is defined as
\begin{equation}
\partial_x^{n+\alpha}f(x)\defeq\frac{1}{\Gamma(1-\alpha)}\int_0^x(x-s)^{-\alpha}f^{(n+1)}(s)ds
\end{equation}
\end{definition}

In particular, this definition is well suited for the differential calculus in the convolutive model $\left(\C[\![\zeta]\!], \ast\right)$. Let $\varphi(z)\defeq\sum_{k\geq 0}a_kz^{-k-1}\in\C[\![z^{-1}]\!]$ be Gevrey $1$, then assuming $a_k=0$ for every $k<n$, the Borel transform of $z^{n+\alpha}\varphi(z)$ can be computed in two different ways: \textbf{[Can we do this when $\varphi$ isn't in $o(z^n)$?]}
\begin{multline}
\label{mod1}
\mathcal{B}\left(z^{n+\alpha}\varphi(z)\right)(\zeta)=\mathcal{B}(z^{\alpha+n})\ast\hat{\varphi}(\zeta)=\int_0^{\zeta}\frac{(\zeta-s)^{-1-n-\alpha}}{(-1-n-\alpha)!}\sum_{k\geq 0}\frac{a_k}{k!}s^{k}ds\\
=\frac{1}{(-\alpha)!}\int_0^{\zeta}(\zeta-s)^{-\alpha}\sum_{k\geq 0}\frac{a_k}{(k-n-1)!}s^{k-n-1}ds=\partial_{\zeta}^{n+\alpha}\hat{\varphi}(\zeta)
\end{multline}
\begin{equation}
\label{mod2}
\mathcal{B}\left(z^{n+\alpha}\varphi(z)\right)(\zeta)=\mathcal{B}\left(\sum_{k\geq 0}a_kz^{-k-1+n+\alpha}\right)(\zeta)=\sum_{k>n}\frac{a_k}{(k-n-\alpha)!}\zeta^{k-n-\alpha}
\end{equation}

and computitng the integral which defines the $n+\alpha$-derivative in \eqref{mod1} we get exaclty the same result as \eqref{mod2}.
\color{black}
\section{Resurgence of exponential integrals}
Let $X$ be a $N-\dim$ manifold, $f\colon X\to\C$ be a holomorphic Morse function with only simple critical points, and $\nu\in\Gamma(X,\Omega^N)$, and set
\begin{equation}
I(z)\defeq\int_{\mathcal{C}}e^{-zf}\nu
\end{equation}
where $\mathcal{C}$ is a suitable countur such that the integral is well defined.  
For any Morse cirtial points $x_\alpha$ of $f$, the saddle point approximation gives the following formal series 
\begin{equation}
I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu\sim \tilde{I}_{\alpha}\defeq e^{-zf(x_\alpha)}(2\pi)^{N/2} z^{-N/2}\sum_{n\geq 0}a_{\alpha,n}z^{-n} \qquad \text{ as } z\to\infty
\end{equation}
where $\mathcal{C}_\alpha$ is a steepest descent path through the critical point $x_\alpha$. Notice that $f \circ \mathcal{C}_\alpha$ lies in the ray $\zeta_\alpha + [0, \infty)$, where $\zeta_\alpha := f(x_\alpha)$.
\begin{theorem}\label{thm:maxim} Let $N=1$. Let $\tilde{\varphi}_{\alpha}(z)\defeq e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}$ and assume $f''(x_\alpha)\neq 0$ for every critical point $x_\alpha$. Then:
\begin{enumerate}
\item The series $\tilde{\varphi}_\alpha$ is Gevrey-1.
\item The series $\hat{\varphi}(\zeta)\defeq\mathcal{B}(\tilde{\varphi})$ converges near $\zeta=\zeta_{\alpha}$.
\item For any $\zeta$ on the ray going rightward from $\zeta_\alpha$, we have
\begin{align*}\label{formula1}
\hat{\varphi}_{\alpha}(\zeta) & = \partial^{\textcolor{red}{3/2}}_{\zeta \text{ from }\zeta_\alpha} \left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right) \\
& = \textcolor{red}{\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-1/2} \textcolor{red}{\left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right)}\,d\zeta',
\end{align*}
where $\mathcal{C}_\alpha(\zeta)$ is the part of $\mathcal{C}_\alpha$ that goes through $f^{-1}([\zeta_\alpha, \zeta])$. Notice that $\mathcal{C}_\alpha(\zeta)$ starts and ends in $f^{-1}(\zeta)$. \textbf{[The integral over $\mathcal{C}_\alpha(\zeta)$ needs to satisfy some condition near $\zeta = 0$ for this to hold. Figure out what that is! Also, be careful about the orientation of $\mathcal{C}_\alpha$.]}
\item
\end{enumerate}
\end{theorem}
\begin{proof}
Part~(1): Let's write $\approx$ when two functions are asymptotic (at all orders around the base point \textbf{[is this the right condition?]}), and $\sim$ when a function is asymptotic to a formal power series (at the truncation order of each partial sum).

@@

and Mathematica gives the following solutions
\begin{align*}
\hat{u}(\zeta)&=c_1 \, {}_{1}F_{2}\left(\frac{7}{12},\frac{11}{12},\frac{1}{2},\frac{9}{4}\zeta^2\right) +\frac{3i}{2}\zeta c_2 \, {}_{1}F_{2}\left(\frac{13}{12},\frac{17}{12},\frac{3}{2},\frac{9}{4}\zeta^2\right)= &\\
&=c_1\frac{\Gamma(\frac{13}{12})\Gamma(\frac{17}{12})}{2\sqrt{\pi}}\left({}_{1}F_{2}\left(\frac{7}{12},\frac{11}{12},\frac{1}{2},\frac{1}{2}-\frac{3}{4}\zeta\right)- {}_{1}F_{2}\left(\frac{7}{12},\frac{11}{12},\frac{1}{2},\frac{1}{2}+\frac{3}{4}\zeta\right)\right) & \text{see DLMF 15.8.27} \\
&\qquad +\frac{3i}{2}\zeta c_2 \left(\frac{\Gamma(\frac{7}{12})\Gamma(\frac{11}{12})}{3\zeta\Gamma(-\frac{1}{2})\Gamma(2)}\right)\left( {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},{2},\frac{1}{2}-\frac{3}{4}\zeta\right)-{}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},{2},\frac{1}{2}+\frac{3}{4}\zeta\right)\right)  & \text{see DLMF 15.8.28}\\
&=\left(c_1\frac{\Gamma(\frac{13}{12})\Gamma(\frac{17}{12})}{2\sqrt{\pi}} -c_2i\frac{\Gamma(\frac{7}{12})\Gamma(\frac{11}{12})}{4\sqrt{\pi}}\right)\, {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,\frac{1}{2}-\frac{3}{4}\zeta\right)  + & \\
&\qquad\qquad +\left(c_1\frac{\Gamma(\frac{13}{12})\Gamma(\frac{17}{12})}{2\sqrt{\pi}} +c_2i\frac{\Gamma(\frac{7}{12})\Gamma(\frac{11}{12})}{4\sqrt{\pi}}\right)\, {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,\frac{1}{2}+\frac{3}{4}\zeta\right) &  
\end{align*}
Since $\hat{u}_+$ has a simple singularity at $\zeta=-2/3$ and $\hat{u}_-$ has a simple singularity at $\zeta=2/3$, we have
\begin{align*}
\hat{u}_+(\zeta)&=C_1 T_{-2/3} {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,-\frac{3}{4}\zeta\right)=C_1 T_{-2/3}\hat{w}_+(\zeta)\\
\hat{u}_-(\zeta)&= C_2 T_{2/3} {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,\frac{3}{4}\zeta\right)= C_2 T_{2/3}\hat{w}_-(\zeta) & \\
%&=C_3 T_{-2/3}\textcolor{red}{\left(\frac{3}{2\sqrt{\zeta}}\right)^{-1}\partial^{1/2}_{\zeta} {}_{1}F_{2}\left(\frac{2}{3},\frac{4}{3},\frac{3}{2},-\frac{3}{4}\zeta\right)}+ C_4\textcolor{red}{\left(\frac{3}{2\sqrt{\zeta}}\right)^{-1}\partial^{1/2}_\zeta {}_{1}F_{2}\left(\frac{2}{3},\frac{4}{3},\frac{3}{2},\frac{3}{4}\zeta\right)}
\end{align*}
%
%\begin{claim}\label{claim1}
%\begin{equation}
%\hat{w}_+(\zeta-2/3)=\frac{1}{\sqrt{\pi}}\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s}\left(\frac{1}{f'(u)}\right)ds \,\,\qquad s=f(u)
%\end{equation}
%\end{claim}

@@

\begin{claim}\label{claim 2}
\textbf{[There should be a way to predict the correct normalization of the LHS.]}
\begin{equation}
\hat{w}_+(\zeta-2/3)=-\frac{1}{\sqrt{\pi}}\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s} \left[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}s^2\right)\right]\,ds \qquad \zeta\in(2/3,+\infty)
\end{equation}
\end{claim}

\color{Turquoise}

@@

\color{MidnightBlue}

@@

\color{violet}
Alternate calculation with $\tfrac{1}{2}$ derivative:
\begin{align*}
&\int_{2/3}^{\zeta}(\zeta-s)^{-1/2} {}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}s^2\right) ds \\
&= \frac{2}{3} \int_{2/3}^{\zeta}(\zeta-s)^{-1/2} \left[ {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{1}{2}-\frac{3s}{4}\right) + {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{1}{2}+\frac{3s}{4}\right) \right] ds & 15.8.27 \text{ DLMF} \\
&=\frac{4}{3\sqrt{3}}\int_0^x(x-y)^{-1/2}\left[ {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};1-y\right) + {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};y\right)\right]dy & x\in (-\infty,0) \\
&=\frac{2i}{3\sqrt{3}}\int_0^x(x-y)^{-1/2}\left[ \big(1+\tfrac{1}{\sqrt{3}}\big) y^{-2/3} {}_2F_1\left(\frac{2}{3}, \frac{1}{6}, \frac{1}{3};\frac{1}{y}\right) + \big(1-\tfrac{1}{\sqrt{3}}\big) y^{-4/3} {}_2F_1\left(\frac{4}{3}, \frac{5}{6}, \frac{5}{3};\frac{1}{y}\right) \right] ds \\
&=\frac{2i}{3\sqrt{3}} \left[ \frac{\Gamma(\tfrac{1}{2})\Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{2}{3})} \big(1+\tfrac{1}{\sqrt{3}}\big) x^{-1/6} {}_2F_1\left(\frac{1}{6}, \frac{1}{6}, \frac{1}{3};\frac{1}{x}\right) + \frac{\Gamma(\tfrac{1}{2})\Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{4}{3})}\big(1-\tfrac{1}{\sqrt{3}}\big) x^{-5/6} {}_2F_1\left(\frac{5}{6}, \frac{5}{6}, \frac{5}{3};\frac{1}{x}\right) \right] ds & \eqref{4.8} \\
&=??? & \zeta\in (2/3,+\infty)
\end{align*}
\color{black}

>>>>

\section{Fractional derivatives and Borel transform}

\begin{definition}
Let $\alpha\in (0,1)$ and $n\in\N$, then the $n+\alpha$-Caputo's derivative of a smooth fucntion $f$ is defined as
\begin{equation}
\partial_x^{n+\alpha}f(x)\defeq\frac{1}{\Gamma(1-\alpha)}\int_0^x(x-s)^{-\alpha}f^{(n+1)}(s)ds
\end{equation}
\end{definition}

In particular, this definition is well suited for the differential calculus in the convolutive model $\left(\C[\![\zeta]\!], \ast\right)$. Let $\varphi(z)\defeq\sum_{k\geq 0}a_kz^{-k-1}\in\C[\![z^{-1}]\!]$ be Gevrey $1$, then assuming $a_k=0$ for every $k<n$, the Borel transform of $z^{n+\alpha}\varphi(z)$ can be computed in two different ways:
\begin{multline}
\label{mod1}
\mathcal{B}\left(z^{n+\alpha}\varphi(z)\right)(\zeta)=\mathcal{B}(z^{\alpha+n})\ast\hat{\varphi}(\zeta)=\int_0^{\zeta}\frac{(\zeta-s)^{-1-n-\alpha}}{(-1-n-\alpha)!}\sum_{k\geq 0}\frac{a_k}{k!}s^{k}ds\\
=\frac{1}{(-\alpha)!}\int_0^{\zeta}(\zeta-s)^{-\alpha}\sum_{k\geq 0}\frac{a_k}{(k-n-1)!}s^{k-n-1}ds=\partial_{\zeta}^{n+\alpha}\hat{\varphi}(\zeta)
\end{multline}
\begin{equation}
\label{mod2}
\mathcal{B}\left(z^{n+\alpha}\varphi(z)\right)(\zeta)=\mathcal{B}\left(\sum_{k\geq 0}a_kz^{-k-1+n+\alpha}\right)(\zeta)=\sum_{k>n}\frac{a_k}{(k-n-\alpha)!}\zeta^{k-n-\alpha}
\end{equation}

and computitng the integral which defines the $n+\alpha$-derivative in \eqref{mod1} we get exaclty the same result as \eqref{mod2}.

\section{Resurgence of exponential integrals}

Let $X$ be a $N-\dim$ manifold, $f\colon X\to\C$ be a holomorphic Morse function with only simple critical points, and $\nu\in\Gamma(X,\Omega^N)$, and set

\begin{equation}
I(z)\defeq\int_{\mathcal{C}}e^{-zf}\nu
\end{equation}
where $\mathcal{C}$ is a suitable countur such that the integral is well defined.  
For any Morse cirtial points $x_\alpha$ of $f$, the saddle point approximation gives the following formal series 
\begin{equation}
I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu\sim \tilde{I}_{\alpha}\defeq e^{-zf(x_\alpha)}(2\pi)^{N/2} z^{-N/2}\sum_{n\geq 0}a_{\alpha,n}z^{-n} \qquad \text{ as } z\to\infty
\end{equation}
where $\mathcal{C}_\alpha$ is a steepest descent path through the critical point $x_\alpha$. Notice that $f \circ \mathcal{C}_\alpha$ lies in the ray $\zeta_\alpha + [0, \infty)$, where $\zeta_\alpha := f(x_\alpha)$.
\begin{theorem}\label{thm:maxim} Let $N=1$. Let $\tilde{\varphi}_{\alpha}(z)\defeq e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}$ and assume $f''(x_\alpha)\neq 0$ for every critical point $x_\alpha$. Then:
\begin{enumerate}
\item The series $\tilde{\varphi}_\alpha$ is Gevrey-1.
\item The series $\hat{\varphi}(\zeta)\defeq\mathcal{B}(\tilde{\varphi})$ converges near $\zeta=\zeta_{\alpha}$.
\item For any $\zeta$ on the ray going rightward from $\zeta_\alpha$, we have
\begin{align*}\label{formula1}
\hat{\varphi}_{\alpha}(\zeta) & = \partial^{\textcolor{red}{3/2}}_{\zeta \text{ from }\zeta_\alpha}\left(\int_{\mathcal{C}_\alpha(\zeta)} \nu \right) \\
& = \Gamma\big(-\tfrac{1}{2}\big)\int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-1/2}\textcolor{red}{\partial_{\zeta'}\left(\left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta')}^{\operatorname{end} \mathcal{C}_\alpha(\zeta')} \right)}\,d\zeta',
\end{align*}
where $\mathcal{C}_\alpha(\zeta)$ is the part of $\mathcal{C}_\alpha$ that goes through $f^{-1}([\zeta_\alpha, \zeta])$. Notice that $\mathcal{C}_\alpha(\zeta)$ starts and ends in $f^{-1}(\zeta)$. \textbf{[Be careful about the orientation of $\mathcal{C}_\alpha$.]}
\item
\end{enumerate}
\end{theorem}
\begin{proof}
Part~(1): Let's write $\approx$ when two functions are asymptotic (at all orders around the base point \textbf{[is this the right condition?]}), and $\sim$ when a function is asymptotic to a formal power series (at the truncation order of each partial sum).

@@

and Mathematica gives the following solutions
\begin{align*}
\hat{u}(\zeta)&=c_1 \, {}_{1}F_{2}\left(\frac{7}{12},\frac{11}{12},\frac{1}{2},\frac{9}{4}\zeta^2\right) +\frac{3i}{2}\zeta c_2 \, {}_{1}F_{2}\left(\frac{13}{12},\frac{17}{12},\frac{3}{2},\frac{9}{4}\zeta^2\right)= &\\
&=c_1\frac{\Gamma(\frac{13}{12})\Gamma(\frac{17}{12})}{2\sqrt{\pi}}\left({}_{1}F_{2}\left(\frac{7}{12},\frac{11}{12},\frac{1}{2},\frac{1}{2}-\frac{3}{4}\zeta\right)- {}_{1}F_{2}\left(\frac{7}{12},\frac{11}{12},\frac{1}{2},\frac{1}{2}+\frac{3}{4}\zeta\right)\right) & \text{see DLMF 15.8.27} \\
&\qquad +\frac{3i}{2}\zeta c_2 \left(\frac{\Gamma(\frac{7}{12})\Gamma(\frac{11}{12})}{3\zeta\Gamma(-\frac{1}{2})\Gamma(2)}\right)\left( {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},{2},\frac{1}{2}-\frac{3}{4}\zeta\right)-{}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},{2},\frac{1}{2}+\frac{3}{4}\zeta\right)\right)  & \text{see DLMF 15.8.28}\\
&=\left(c_1\frac{\Gamma(\frac{13}{12})\Gamma(\frac{17}{12})}{2\sqrt{\pi}} -c_2i\frac{\Gamma(\frac{7}{12})\Gamma(\frac{11}{12})}{4\sqrt{\pi}}\right)\, {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,\frac{1}{2}-\frac{3}{4}\zeta\right)  + & \\
&\qquad\qquad +\left(c_1\frac{\Gamma(\frac{13}{12})\Gamma(\frac{17}{12})}{2\sqrt{\pi}} +c_2i\frac{\Gamma(\frac{7}{12})\Gamma(\frac{11}{12})}{4\sqrt{\pi}}\right)\, {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,\frac{1}{2}+\frac{3}{4}\zeta\right) &  
\end{align*}
Since $\hat{u}_+$ has a simple singularity at $\zeta=-2/3$ and $\hat{u}_-$ has a simple singularity at $\zeta=2/3$, we have
\begin{align*}
\hat{u}_+(\zeta)&=C_1 T_{-\tfrac{2}{3}}\,\, {}_{2}F_{1}\left(\frac{7}{6},\frac{11}{6},2,-\frac{3}{4}\zeta\right)=C_1 T_{-\tfrac{2}{3}}\,\,\hat{w}_+(\zeta)\\
\hat{u}_-(\zeta)&= C_2 T_{\tfrac{2}{3}}\,\, {}_{2}F_{1}\left(\frac{7}{6},\frac{11}{6},2,\frac{3}{4}\zeta\right)= C_2 T_{\tfrac{2}{3}}\,\,\hat{w}_-(\zeta) & \\
%&=C_3 T_{-2/3}\textcolor{red}{\left(\frac{3}{2\sqrt{\zeta}}\right)^{-1}\partial^{1/2}_{\zeta} {}_{2}F_{1}\left(\frac{2}{3},\frac{4}{3},\frac{3}{2},-\frac{3}{4}\zeta\right)}+ C_4\textcolor{red}{\left(\frac{3}{2\sqrt{\zeta}}\right)^{-1}\partial^{1/2}_\zeta {}_{2}F_{1}\left(\frac{2}{3},\frac{4}{3},\frac{3}{2},\frac{3}{4}\zeta\right)}
\end{align*}
%
%\begin{claim}\label{claim1}
%\begin{equation}
%\hat{w}_+(\zeta-2/3)=\frac{1}{\sqrt{\pi}}\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s}\left(\frac{1}{f'(u)}\right)ds \,\,\qquad s=f(u)
%\end{equation}
%\end{claim}

@@

\begin{claim}\label{claim 2}
\textbf{[There should be a way to predict the correct normalization of the LHS.]}
\begin{equation}
\hat{w}_+(\zeta-2/3)=-\frac{1}{\sqrt{\pi}}\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s}\left[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}s^2\right)\right]ds \qquad \zeta\in(2/3,+\infty)
\end{equation}
\end{claim}

\color{violet}

@@

\color{black}

@@

\textcolor{violet}{
Alternate calculation with $\tfrac{1}{2}$ derivative:
\begin{align*}
&\int_{2/3}^{\zeta}(\zeta-s)^{-1/2} {}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}s^2\right) ds \\
&= \frac{2}{3} \int_{2/3}^{\zeta}(\zeta-s)^{-1/2} \left[ {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{1}{2}-\frac{3s}{4}\right) + {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{1}{2}+\frac{3s}{4}\right) \right] ds & 15.8.27 \text{ DLMF} \\
&=\frac{4}{3\sqrt{3}}\int_0^x(x-y)^{-1/2}\left[ {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};1-y\right) + {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};y\right)\right]dy & x\in (-\infty,0) \\
&=\frac{2i}{3\sqrt{3}}\int_0^x(x-y)^{-1/2}\left[ \big(1+\tfrac{1}{\sqrt{3}}\big) y^{-2/3} {}_2F_1\left(\frac{2}{3}, \frac{1}{6}, \frac{1}{3};\frac{1}{y}\right) + \big(1-\tfrac{1}{\sqrt{3}}\big) y^{-4/3} {}_2F_1\left(\frac{4}{3}, \frac{5}{6}, \frac{5}{3};\frac{1}{y}\right) \right] ds \\
&=\frac{2i}{3\sqrt{3}} \left[ \frac{\Gamma(\tfrac{1}{2})\Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{2}{3})} \big(1+\tfrac{1}{\sqrt{3}}\big) x^{-1/6} {}_2F_1\left(\frac{1}{6}, \frac{1}{6}, \frac{1}{3};\frac{1}{x}\right) + \frac{\Gamma(\tfrac{1}{2})\Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{4}{3})}\big(1-\tfrac{1}{\sqrt{3}}\big) x^{-5/6} {}_2F_1\left(\frac{5}{6}, \frac{5}{6}, \frac{5}{3};\frac{1}{x}\right) \right] ds & \eqref{4.8} \\
&=??? & \zeta\in (2/3,+\infty)
\end{align*}
}

Analougusly, it can be verified for $\hat{w}_-(\zeta+2/3)$ for $\zeta\in(-\infty,-2/3)$.  
%By definition ${}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};t\right)=\sum_{n\geq 0}\frac{(2/3)_n(4/3)_n}{(3/2)_n n!}t^n$, thus
%
%\begin{align*}
%\int_{0}^{\zeta''}(\zeta''-t)^{-1/2} {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};t\right)dt=\sqrt{\pi}\sum_{n\geq 0}\frac{(2/3)_n(4/3)_n}{(3/2)_n \Gamma(3/2+n)}{\zeta''}^{n+\frac{1}{2}}= 2\sqrt{\zeta''}{}_3F_2\left(\frac{2}{3},\frac{4}{3},1;\frac{3}{2},\frac{3}{2};\zeta''\right)\\
%\int_{1}^{\zeta'}(\zeta'-t)^{-1/2} {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};t\right)dt= 2\sqrt{\zeta'}{}_3F_2\left(\frac{2}{3},\frac{4}{3},1;\frac{3}{2},\frac{3}{2};\zeta'\right)-\int_0^1(\zeta'-t)^{-1/2} {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};t\right)dt
%\end{align*}
